Normalization: A pipeline to analyse time-course gene expression data

### 2019-02-23 scripts/01_quality_control_normalization.Rmd
More text on the QC normalization section

@@

aheatmap(data_corr,
         Colv=NA, Rowv=NA,
         annCol=meta[,
		     c("Group", "Time",
		       "Replicate")],
         annLegend=FALSE, 
	 annColors=ann_colors,
         main="Correlation plot")
```

We can already see interesting patterns: the cross-correlation amongst samples
taking from the untreated mice is higher than the cross correlation amongst
the rest of the treatments.

## Structure of the data set

```{r}
```

>>>>

Before performing any additional exploratory analysis, let us only keep highly
variable genes.

```{r}
variance_cutoff = 0.5
variance_per_genes = apply(data, 1, mad)
min_variance = quantile(variance_per_genes, c(variance_cutoff))
data = data[variance_per_genes > min_variance,]
```

```{r echo=FALSE, fig.width=8, fig.height=4}
hist(variance_per_genes, breaks=100, col="black", xlab="Variance",
     ylab="# probes")
abline(v=min_variance, col="#AB0000", lw=2)
```

@@

meta$Time = as.factor(meta$Time)
aheatmap(data_corr,
         Colv=NA, Rowv=NA,
         annCol=meta[,
		     c("Group", "Time")],
         annLegend=FALSE, 
	 annColors=ann_colors,
         main="Correlation plot")
```

We can already see interesting patterns emerging from the correlation plot.
First, the cross-correlation amongst samples taking from the control mice is
higher than the cross correlation amongst the rest of the treatments. Second,
the influenza-infected mice midly react until time point 36. Third, the
California strain samples seem closer to control samples than the
lowly-pathogenic Kawasaki samples. Fourth, the Vietnam samples at time point
120 and 168 are the one that are the most different from control samples.
